KV Analysis for Non-Expressive performances

### 2021-07-05 material/expstimuli/analysis/stim_n/duration.Rmd
bar plots >> box plots
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@

# ggplots
theme_set(theme_classic())
theme_update(text = element_text(size = 20, family = "Helvetica Neue LT Std 57 Condensed"), legend.position = "bottom")
```

@@

### Plot
#### Bar chart
- Error bars show SD of the mean

```{r duration_bar,  echo = FALSE}
p_duration <- ggplot(data = duration, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  labs(y = "Normalised Duration", subtitle = "Duration: Non-Expression")
p_duration
```

@@

```{r outlier, echo = FALSE}
excluded_duration <- duration[Mean < duration_all$Mean+3*duration_all$SD & Mean > duration_all$Mean-3*duration_all$SD]
print(excluded_duration)
```
- The number of excluded performance: `r duration_all$N-nrow(excluded_duration)`

@@

```{r cv, echo = FALSE}
# for each participant
cv <- dt_duration[EighthNote == "Yes", .(N = length(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)]
print(cv)
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

@@

```{r cv_outlier, echo = FALSE}
excluded_cv <- cv[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

>>>>

- Last checked: `r format(Sys.Date(), "%d-%b-%Y")`

@@

# ggplots
theme_set(theme_classic())
theme_update(legend.position = "bottom")
```

@@

### Plot
#### Box plot

```{r duration_bar,  echo = FALSE}
duration_trial <- dt_duration[EighthNote == "Yes", .(N = length(normDu), Mean = mean(normDu), SD = sd(normDu)), by = .(SubNr, TrialNr)]

p_duration <- ggplot(data = duration_trial, aes(x = SubNr, y = Mean)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) +
  labs(y = "Normalised Duration", subtitle = "Duration: Non-Expression")
p_duration
```

@@

```{r outlier, echo = FALSE}
excluded_duration <- duration_trial[Mean < duration_all$Mean+3*duration_all$SD & Mean > duration_all$Mean-3*duration_all$SD]
print(excluded_duration)
```
- The number of excluded performance: `r nrow(duration_trial)-nrow(excluded_duration)`

@@

```{r cv, echo = FALSE}
# for each participant
cv <- dt_duration[EighthNote == "Yes", .(N = length(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr)]
print(cv)
```

```{r cv_box, echo = FALSE}
cv_trial <- dt_duration[EighthNote == "Yes", .(N = length(normDu), CV = sd(normDu)/mean(normDu)), by = .(SubNr, TrialNr)]

p_cv_box <- ggplot(cv_trial, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

@@

```{r cv_outlier, echo = FALSE}
excluded_cv <- cv_trial[CV < cv_all$Mean+3*(cv_all$SD) & CV > cv_all$Mean-3*cv_all$SD]
print(excluded_cv)
```
- The number of excluded performance: `r cv_all$N-nrow(excluded_cv)`

### 2021-07-05 material/expstimuli/analysis/stim_n/kv.Rmd
bar plots >> box plots
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Plot
#### Bar chart
- Error bars show SD of the mean

```{r kv_bar,  echo = FALSE}
p_kv <- ggplot(data = kv, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  labs(y = "Key Velocity", subtitle = "KV: Non-Expression")
p_kv
```

@@

```{r outlier, echo = FALSE}
excluded_kv <- kv[Mean < kv_all$Mean+3*kv_all$SD & Mean > kv_all$Mean-3*kv_all$SD]
print(excluded_kv)
```
- The number of excluded performance: `r kv_all$N-nrow(excluded_kv)`

@@

```{r cv, echo = FALSE}
# for each participant
cv <- dt_kv[EighthNote == "Yes", .(N = length(Velocity), CV = sd(Velocity)/mean(Velocity)) , by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

>>>>

### Plot
#### Box plot

```{r kv_bar,  echo = FALSE}
kv_trial <- dt_kv[EighthNote == "Yes", .(N = length(Velocity), Mean = mean(Velocity), SD = sd(Velocity)), by = .(SubNr, TrialNr)]

p_kv <- ggplot(data = kv_trial, aes(x = SubNr, y = Mean)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5) +
  labs(y = "Key Velocity", subtitle = "KV: Non-Expression")
p_kv
```

@@

```{r outlier, echo = FALSE}
excluded_kv <- kv_trial[Mean < kv_all$Mean+3*kv_all$SD & Mean > kv_all$Mean-3*kv_all$SD]
print(excluded_kv)
```
- The number of excluded performance: `r nrow(kv_trial)-nrow(excluded_kv)`

@@

```{r cv, echo = FALSE}
# for each participant
cv <- dt_kv[EighthNote == "Yes", .(N = length(Velocity), CV = sd(Velocity)/mean(Velocity)) , by = .(SubNr)]
cv
```

#### Box plot
```{r cv_box, echo = FALSE}
cv_trial <- dt_kv[EighthNote == "Yes", .(N = length(Velocity), CV = sd(Velocity)/mean(Velocity)) , by = .(SubNr, TrialNr)]

p_cv_box <- ggplot(cv_trial, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```
